---
title: "weihao Li part"
author: "Liweihao"
date: "11/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Correlation coefficient
Maximal information coefficient
Spearman correlation 
Kemdall correlation

cor(x, y, method = c("pearson", "kendall", "spearman"))

```{r}
library(knockoff)
library(minerva)
library(MASS)
```

Fixed-X case: linear model

```{r}


result_VIM_cor_fixed_X<-function(p=200,n=500,k=40,fdr=0.1,Nreplicate=100){
  result_FDP_est=data.frame()
  result_power=data.frame()
  for(i in 1:Nreplicate){
    # create data, row of X follow multivariate normal with mean 0 Cov=diagonal matrix
    mu = rep(0,p); Sigma = 4*diag(p)
    nonzero = sort(sample(p, k))
    X = mvrnorm(n,mu,Sigma)
    #beta=rnorm(p,sd=3); beta[-nonzero]=0
    beta = 3.5 * (1:p %in% nonzero)
    y = X %*% beta + rnorm(n)
    
    knockoff_X=create.fixed(X)
    X=knockoff_X$X
    X_tilde=knockoff_X$Xk
    
    pearson_W=sapply(1:p,function(j) {abs(sum(y*X[,j]))-abs(sum(y*X_tilde[,j]))})
    kendall_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("kendall")))-abs(cor(y,X_tilde[,j],method = c("kendall")))})
    spearman_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("spearman")))-abs(cor(y,X_tilde[,j],method = c("spearman")))})
    MIC_W=sapply(1:p,function(j){mine(y,X[,j])$MIC-mine(y,X_tilde[,j])$MIC})
    thres_pearson=knockoff.threshold( pearson_W,fdr); discoveries_pearson = which(pearson_W > thres_pearson)
    thres_kendall=knockoff.threshold( kendall_W,fdr); discoveries_kendall = which(kendall_W > thres_kendall)
    thres_spearman=knockoff.threshold(spearman_W,fdr);discoveries_spearman=which(spearman_W>thres_spearman)
    thres_MIC=knockoff.threshold(MIC_W,fdr); discoveries_MIC=which(MIC_W>thres_MIC)
    fdp_one_time=c(sum(1 - discoveries_pearson %in% nonzero)/max(1,length(discoveries_pearson)),
                   sum(1 - discoveries_kendall %in% nonzero)/max(1,length(discoveries_kendall)),
                   sum(1 - discoveries_spearman %in% nonzero)/max(1,length(discoveries_spearman)),
                   sum(1 - discoveries_MIC %in% nonzero)/max(1,length(discoveries_MIC)))
    power_one_time=c(sum( discoveries_pearson %in% nonzero)/k,
                   sum( discoveries_kendall %in% nonzero)/k,
                   sum( discoveries_spearman %in% nonzero)/k,
                   sum(discoveries_MIC %in% nonzero)/k)
    result_power=rbind(result_power,power_one_time)
    result_FDP_est=rbind(result_FDP_est,fdp_one_time)
  }
  colnames(result_power)=c("pearson","kendall","spearman","MIC")
  colnames(result_FDP_est)=c("pearson","kendall","spearman","MIC")
  return(list(power=result_power,fdp=result_FDP_est))
  
}
result=result_VIM_cor_fixed_X(Nreplicate = 5)
result$fdp
result$power
```


Model-X case: linear model
```{r}
result_VIM_cor_Model_X_linear<-function(p=100,n=300,k=20,fdr=0.1,Nreplicate=100){
  result_FDP_est=data.frame()
  for(i in 1:Nreplicate){
    # create data, row of X follow multivariate normal with mean 0 Cov=diagonal matrix
    mu=rep(0,p); Sigma=toeplitz(0.3^(0:(p-1)))
    X = mvrnorm(n,mu,Sigma)
    X_tilde = create.gaussian(X, mu, Sigma)
    nonzero = sort(sample(p, k))
    beta=rnorm(p,sd=3); beta[-nonzero]=0
    #beta = 3.5 * (1:p %in% nonzero)
    y = X %*% beta + rnorm(n)
    pearson_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("pearson")))-abs(cor(y,X_tilde[,j],method = c("pearson")))})
    kendall_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("kendall")))-abs(cor(y,X_tilde[,j],method = c("kendall")))})
    spearman_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("spearman")))-abs(cor(y,X_tilde[,j],method = c("spearman")))})
    MIC_W=sapply(1:p,function(j){mine(y,X[,j])$MIC-mine(y,X_tilde[,j])$MIC})
    thres_pearson=knockoff.threshold( pearson_W,fdr); discoveries_pearson = which(pearson_W > thres_pearson)
    thres_kendall=knockoff.threshold( kendall_W,fdr); discoveries_kendall = which(kendall_W > thres_kendall)
    thres_spearman=knockoff.threshold(spearman_W,fdr);discoveries_spearman=which(spearman_W>thres_spearman)
    thres_MIC=knockoff.threshold(MIC_W,fdr); discoveries_MIC=which(MIC_W>thres_MIC)
    fdp_one_time=c(sum(1 - discoveries_pearson %in% nonzero)/max(1,length(discoveries_pearson)),
                   sum(1 - discoveries_kendall %in% nonzero)/max(1,length(discoveries_kendall)),
                   sum(1 - discoveries_spearman %in% nonzero)/max(1,length(discoveries_spearman)),
                   sum(1 - discoveries_MIC %in% nonzero)/max(1,length(discoveries_MIC)))
    result_FDP_est=rbind(result_FDP_est,fdp_one_time)
  }
  colnames(result_FDP_est)=c("pearson","kendall","spearman","MIC")
  result_FDP_est
  
}
result_VIM_cor_Model_X_linear(k=30,fdr = 0.1,Nreplicate = 5)
```

Model-X case: logistics model
```{r}
result_VIM_cor_Model_X_logistic<-function(p=100,n=300,k=20,fdr=0.1,Nreplicate=100){
  result_FDP_est=data.frame()
  for(i in 1:Nreplicate){
    # create data, row of X follow multivariate normal with mean 0 Cov=diagonal matrix
    mu=rep(0,p); Sigma=toeplitz(0.3^(0:(p-1)))
    X = mvrnorm(n,mu,Sigma)
    X_tilde = create.gaussian(X, mu, Sigma)
    nonzero = sort(sample(p, k))
    beta=rnorm(p,sd=3); beta[-nonzero]=0
    #beta = 3.5 * (1:p %in% nonzero)
    y = X %*% beta + rnorm(n)
    pearson_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("pearson")))-abs(cor(y,X_tilde[,j],method = c("pearson")))})
    kendall_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("kendall")))-abs(cor(y,X_tilde[,j],method = c("kendall")))})
    spearman_W=sapply(1:p,function(j) {abs(cor(y,X[,j],method = c("spearman")))-abs(cor(y,X_tilde[,j],method = c("spearman")))})
    MIC_W=sapply(1:p,function(j){mine(y,X[,j])$MIC-mine(y,X_tilde[,j])$MIC})
    thres_pearson=knockoff.threshold( pearson_W,fdr); discoveries_pearson = which(pearson_W > thres_pearson)
    thres_kendall=knockoff.threshold( kendall_W,fdr); discoveries_kendall = which(kendall_W > thres_kendall)
    thres_spearman=knockoff.threshold(spearman_W,fdr);discoveries_spearman=which(spearman_W>thres_spearman)
    thres_MIC=knockoff.threshold(MIC_W,fdr); discoveries_MIC=which(MIC_W>thres_MIC)
    fdp_one_time=c(sum(1 - discoveries_pearson %in% nonzero)/max(1,length(discoveries_pearson)),
                   sum(1 - discoveries_kendall %in% nonzero)/max(1,length(discoveries_kendall)),
                   sum(1 - discoveries_spearman %in% nonzero)/max(1,length(discoveries_spearman)),
                   sum(1 - discoveries_MIC %in% nonzero)/max(1,length(discoveries_MIC)))
    result_FDP_est=rbind(result_FDP_est,fdp_one_time)
  }
  colnames(result_FDP_est)=c("pearson","kendall","spearman","MIC")
  result_FDP_est
  
}
result_VIM_cor_Model_X_linear(fdr = 0.1,Nreplicate = 5)